---
title: "Preparing the MINDACT dataset"
author: "Mary Ann Binuya"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
#Set libpath
#.libPaths(c("U:/libraries", .libPaths()))

knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = FALSE,
  fig.retina = 3,
  fig.path = "Output/1 Data Prep/")

#Load libraries
library(survival) #for data splitting
library(dplyr) #for data manipulations
library(mice) #for imputations
library(cmprsk) #for competing risk analysis
library(riskRegression) #for fgr 
library(cmprsk) #for fgr
library(lava) #for fgr
library(prodlim) #for fgr
library(survminer) #for ggsurvplot
library(coxme) #for mixed effect Cox model

rm(list=ls())
```

# Aim(s)
1. To import and prepare MINDACT dataset
2. To create imputed MINDACT dataset(s)
3. To run PREDICT on imputed MINDACT dataset(s)
4. To check significance of genomic risk for predicting competing events (breast cancer and other deaths)
5. To check proportionality of hazards
6. To check linearity of continuous variables
7. To check if it is necessary to adjust for country
8. To check if genomic risk effect is modified by other risk factors

# 1. Import and prepare dataset
```{r Prep}
# Load data
  mindact <- readxl::read_excel("Data/10041_MIND001_002_transfer.xlsx")
 
  data <- mindact %>%
    select(patid_rand, #Patient IDs to check number of unique records
           tables_AP2,#Group: corrected risk
           Country, #Country, for sensitivity analysis
           clinical_risk, #Adjuvant! Online risk (uncorrected)
           clinical_risk_crg, #Adjuvant! Online risk (corrected)
           genomic_risk, #Genomic risk (uncorrected)
           genomic_risk_crg, #Genomic risk (corrected)
           age, #Age at diagnosis
           meno_MV, #Menopausal status
           tsizecrg, #Tumor size in mm
           tgradpr, tgradelcrg, #Histological grade central and local
           lnstatuscrg, #Number of positive nodes
           er_strict, erstatcrg, #ER status central and local
           pgr_strict, pgrstatcrg, #PR status central and local
           her_bin, her2_local, #Her2 central and local
           ki67_3, #Ki67 status
           chemo_trt2, #Chemotherapy
           adj_ht, #Hormone therapy
           adj_tras, #Anti-HER2 therapy
           OS, OS_CR, OStime) %>% #Overall survival, Overall survival (competing risk), Follow-up time
   rename(pid = patid_rand,
          rgroup = tables_AP2,
          country=Country,
          crisk_ao=clinical_risk_crg,
          grisk=genomic_risk_crg,
          age.start=age,
          menop=meno_MV,
          size=tsizecrg,
          grade_central=tgradpr,
          grade_local=tgradelcrg,
          nodes=lnstatuscrg,
          er_central=er_strict,
          er_local=erstatcrg,
          pr_central=pgr_strict,
          pr_local=pgrstatcrg,
          her2_central=her_bin,
          ki67=ki67_3,
          chemo=chemo_trt2,
          horm=adj_ht,
          traz=adj_tras,
          os=OS,
          oscr=OS_CR,
          time=OStime) %>%
    mutate(eventbc = ifelse(oscr==1, 1, 0), #BC events
           eventoth = ifelse(oscr==2, 1, 0)) #Other events

# Explore data
  n_distinct(data$pid) #6693 unique IDs/patients
  
  #country
  table(data$country, useNA="always") #no missing
  
  #age
  data$age.start <- round(data$age.start,0)
  table(data$age.start, useNA="always") #no missing; 3 patients outside of PREDICT recommended range (25-85) but close enough so retain
  
  #menopausal status (relevant for bisphosphonates use)
  table(data$menop, useNA="always") #251 missing
  
  #size in mm
  table(data$size, useNA="always") #no missing but 1 patient with size=0, confirmed DCIS; exclude
  
    data$er_local[data$size=="0"] #patient with size=0 is ER+, which will cause the breast cancer specific linear predictor of PREDICT to be -Inf; exclude
    
  #grade - use central lab, otherwise (if missing) use local to be consistent with previous MINDACT analysis
  data$grade <- ifelse(!is.na(data$grade_central), data$grade_central, data$grade_local)
  table(data$grade, useNA="always") #11 missing, recode as NA
  data$grade[data$grade==9] <- NA
  
  #nodes - note: category 4 is 4+ nodes
  table(data$nodes, useNA="always") #1 missing
  
  #er status - use central lab, otherwise (if missing) use local
  data$er <- ifelse(!is.na(data$er_central), data$er_central, data$er_local) #1% cut-off per protocol
  table(data$er, useNA="always") #no missing
  
  #pr status - use central lab, otherwise (if missing) use local
  data$pr <- ifelse(!is.na(data$pr_central), data$pr_central, data$pr_local) #1% cut-off per protocol
  table(data$pr, data$er, useNA="always") #1 missing (ER+)
  
  #her2 status - use central lab, otherwise (if missing) use local
  data$her2 <- ifelse(!is.na(data$her2_central), data$her2_central, data$her2_local)
  table(data$her2, useNA="always") #2 missing
  
  #ki67 status - note: cut-offs are 14%, 20%% (PREDICT uses cut off of 10%)
  data$ki67[data$ki67==2] <- 1 #combine levels above 14%
  table(data$ki67, useNA="always") #841 missing
  
  #chemotherapy generation
  data$generation <- ifelse(data$chemo==3|data$chemo==4, 3, data$chemo) #taxane-based regimens
  data$generation[data$chemo==5] <- NA #recode other/unknown to NAs
  table(data$generation, useNA="always") #220 missing chemo; exclude 9 patients treated with first generation chemo as PREDICT doesn"t allow this; moreover, missing patients are unlikely to be treated with first gen (year of diagnosis: 2007-11; while around 2001 taxanes (3rd gen) were already available for treatment of advanced breast cancer)

  #hormone therapy
  table(data$horm, useNA="always") #117 missing
  
  #anti-HER2/trastuzumab therapy
  table(data$traz, useNA="always") #112 missing
  
  #crisk
  table(data$crisk_ao, useNA="always") #1 missing
  data$crisk_ao[is.na(data$crisk_ao)] <- 0 #recode to low per MINDACT codebook
  
  #grisk
  table(data$grisk, useNA="always") #1 missing
  data$grisk[is.na(data$grisk)] <- 0 #recode to low per MINDACT codebook
  
    #noted: 176 (2.6%) discrepancies between corrected and uncorrected grisk --> use corrected risks
    table(data$grisk, data$genomic_risk, useNA="always")
  
  #follow-up time
  data$time <- round(data$time/365.25,2) #convert days to years
  data$time <- ifelse(data$time == 0, 0.003, data$time) #2 patients with time=0 years actually died after 1 day, corrected
    
# Create the variables needed in PREDICT but not available in MINDACT
  #method of screening
  data$screen <- 2 #assume unknown for all
  
  #bisphophonates
  data$bis <- NA
  data$bis <- ifelse(data$menop==2, 1, ifelse(data$menop==1, 0, data$bis)) #assume post-menopausal women received bisphosphonates
  data$bis[is.na(data$bis)&data$age.start>50] <- 1 #use 50 as age cut off for menopause
  data$bis[is.na(data$bis)&data$age.start<=50] <- 0
  table(data$bis, useNA="always")

# Retain only eligible records per above
  dataelig <- data %>%
    filter(size > 0, #exclude 1 DCIS patient with size=0
           generation != 1 | is.na(generation)) #exclude 9 patients treated with first generation chemo
  
    table(dataelig$oscr[dataelig$er==0], dataelig$grisk[dataelig$er==0], useNA="always") #note: zero breast cancer deaths in low risk MammaPrint category for ER-negative tumors
    table(dataelig$oscr[dataelig$er==1], dataelig$grisk[dataelig$er==1], useNA="always")
  
# Retain only variables relevant for subsequent analysis
  dataimp <- dataelig %>%
    filter (er == 1) %>% #limit to ER+ patients
    select(country, grisk, age.start, screen, size, grade, nodes, er, pr, her2, ki67,
           generation, horm, traz, bis, os, oscr, time, eventbc, eventoth)
```

# 2. Create imputed dataset(s)
```{r Imp}
# Check missingness pattern
  md.pattern(dataimp, rotate.names = TRUE) #assume MAR

# Reformat variables
  dataimp[, c("country", "grisk", "er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")] <- lapply(dataimp[, c("country", "grisk", "er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")], FUN=as.factor) #you can also use unclass() and assign class per variable but this is faster

# Calculate marginal baseline cumhaz
  dataimp$cumhaz_bc <- nelsonaalen(dataimp, time, eventbc)
  dataimp$cumhaz_oth <- nelsonaalen(dataimp, time, eventoth)

# Imputation
  ini <- mice(dataimp, maxit=0)
  ini$nmis #number of missing per variable
  
  vis <- c("nodes", "pr", "her2", "grade", "traz", "horm", "generation", "ki67") #define order of imputation; alternatively, you can also just manually change the order of the columns
  
  method <- ini$method #check appropriate methods are used per variable
  method
  
  pred_bc <- ini$predictorMatrix
  pred_bc[,"screen"] <- 0 #exclude, constant
  pred_bc[,"bis"] <- 0 #exclude, derived variable
  pred_bc[,"os"] <- 0
  pred_bc[,"oscr"] <- 0
  pred_bc[,"eventoth"] <- 0
  pred_bc[,"cumhaz_oth"] <- 0
  pred_bc #keep as predictors: survival time, status indicator, baseline cumhaz, and relevant covariates

  
  pred_oth <- ini$predictorMatrix
  pred_oth[,"screen"] <- 0 #exclude, constant
  pred_oth[,"bis"] <- 0 #exclude, derived variable
  pred_oth[,"os"] <- 0
  pred_oth[,"oscr"] <- 0
  pred_oth[,"eventbc"] <- 0
  pred_oth[,"cumhaz_bc"] <- 0
  pred_oth #keep as predictors survival time, status indicator, baseline cumhaz, and relevant covariates

# Impute separately for each competing event
  
  #Breast cancer deaths
  imp_bc <- mice(dataimp, m=20, visitSequence = vis, method=method, predictorMatrix=pred_bc, seed=202309) #FMI~0.2=20 imputations (see White, Royston, Wood, 2011)
    
  sapply(complete(imp_bc), function(x) sum(is.na(x))) #check no more missing
  plot(imp_bc) #check convergence is ok
  densityplot(imp_bc, ~grade+ki67+generation+horm+traz) #check distribution of original (blue) and imputed (red) data; note nodes, her2, and pr not in plot (only one missing each); also note levels are not correctly presented (this is not an error in imputed values, it is just the way MICE creates labels).
  
  imp_oth <- mice(dataimp, m=20, visitSequence = vis, method=method, predictorMatrix=pred_oth, seed=202309)
  
  #Other deaths
  sapply(complete(imp_oth), function(x) sum(is.na(x)))
  plot(imp_oth)
  densityplot(imp_oth, ~grade+ki67+generation+horm+traz)

  rm(ini, pred_bc, pred_oth, method, vis)
```

# 3. Run PREDICT on imputed dataset(s)
```{r PREDICT}
# Load PREDICT version 2.3 function
source("Functions/predictv23_batchrunner.R")

# Run PREDICT on imp_bc
  datapredimp_bc <- complete(imp_bc, action="long", include=TRUE) #complete imputed data

  datapredimp_bc[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")] <- as.numeric(as.matrix(datapredimp_bc[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")])) #format variables for PREDICT function
  
  datapredimp_bc <- ukpredict(datapredimp_bc, year=5, age.start=age.start, screen=screen, size=size, grade=grade, nodes=nodes, er=er, pr=pr, her2=her2, ki67=ki67, generation=generation, horm=horm, traz=traz, bis=bis)
  
  datapredimp_bc[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")] <- lapply(datapredimp_bc[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")], FUN=as.factor) #format variables back
  
  imppred_bc <- as.mids(datapredimp_bc)
  
# Run PREDICT on imp_oth
  datapredimp_oth <- complete(imp_oth, action="long", include=TRUE) #complete imputed data
  
  datapredimp_oth[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")] <- as.numeric(as.matrix(datapredimp_oth[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")])) #format variables for PREDICT function
  
  datapredimp_oth <- ukpredict(datapredimp_oth, year=5, age.start=age.start, screen=screen, size=size, grade=grade, nodes=nodes, er=er, pr=pr, her2=her2, ki67=ki67, generation=generation, horm=horm, traz=traz, bis=bis)
  
  datapredimp_oth[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")] <- lapply(datapredimp_oth[, c("er", "pr", "her2", "ki67", "generation", "horm", "traz", "bis")], FUN=as.factor) #format variables back
  
  imppred_oth <- as.mids(datapredimp_oth)

  rm(list=setdiff(ls(), c("datapredimp_bc", "datapredimp_oth", "imppred_bc", "imppred_oth")))
```

# 4. Check significance of genomic risk for predicting competing events
```{r Outcomes}
# PREDICT considers two competing events in predicting overall mortality (survival): breast cancer-specific and other/unknown deaths. We check if MammaPrint is a significant predictor for both events.

  #Breast cancer
    fit_bcss <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk))
    summary(pool(fit_bcss)) #grisk/MammaPrint a significant predictor for breast cancer death

    fit_bcss_m <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + grisk))
    summary(pool(fit_bcss_m)) #grisk/MammaPrint a significant predictor for breast cancer death after adjustment for PREDICT prognostic index
    
  #Other
    fit_oth <- imppred_oth %>% with(coxph(Surv(time, eventoth) ~ grisk))
    summary(pool(fit_oth)) #grisk/MammaPrint not a significant predictor for other/unknown death
    
    fit_oth_m <- imppred_oth %>% with(coxph(Surv(time, eventoth) ~ mi + grisk))
    summary(pool(fit_oth_m)) #grisk/MammaPrint not a significant predictor for other/unknown death for PREDICT prognostic index
    
    rm(list=ls(pattern="^fit"))
  
# Do a sanity check using subdistribution hazard models instead of cause-specific models
  #Breast cancer
    fgr_res <- fgr_res_m <- list()

    for (i in 1:20) {
      df <- datapredimp_bc %>% filter(.imp == i)
      fgr_bcss <- FGR(Hist(time, oscr) ~ grisk, cause = 1, data = df) #note: FGR ignores offset unlike coxph
      fgr_res[[i]] <- summary(fgr_bcss)$coef
      
      fgr_bcss_m <- FGR(Hist(time, oscr) ~ pirx + grisk, cause = 1, data = df)
      fgr_res_m[[i]] <- summary(fgr_bcss_m)$coef
    }
    
    rand <- sample(1:20, 1)
    fgr_res[[rand]] #same results as cause-specific model, likely due to low event rates = almost similar risk sets
    fgr_res_m[[rand]] #same results as cause-specific model, likely due to low event rates = almost similar risk sets
    
    rm(list=ls(pattern="^fgr"))
    
  #Other - subdistribution models
    fgr_res <- fgr_res_m <- list()

    for (i in 1:20) {
      df <- datapredimp_bc %>% filter(.imp == i)
      fgr_oths <- FGR(Hist(time, oscr) ~ grisk, cause = 2, data = df)
      fgr_res[[i]] <- summary(fgr_oths)$coef
      
      fgr_oths_m <- FGR(Hist(time, oscr) ~ mi + grisk, cause = 2, data = df)
      fgr_res_m[[i]] <- summary(fgr_oths_m)$coef
    }
    
    fgr_res[[rand]] #same results as cause-specific model, likely due to low event rates = almost similar risk sets
    fgr_res_m[[rand]] #same results as cause-specific model, likely due to low event rates = almost similar risk sets
    
    rm(list=ls(pattern="^fgr"))
    rm(df)
    
# Mammaprint not significant for predicting other deaths (other deaths-specific formula remains the same). Limit analysis to breast cancer-specific deaths.
```

# 5. Check proportionality of hazards
```{r PH}
zph_full <- list()

for (i in 1:20) {
  dat <- datapredimp_bc %>%
    filter(.imp == i) %>%
    select(time, eventbc,
           grisk, pirx, age.start, size, grade, nodes, pr, her2, ki67, generation, horm, traz, bis)
  
  fit_bc_full <- coxph(Surv(time, eventbc) ~ ., data = dat) #include all covariates
  res_full <- cox.zph(fit_bc_full, transform = "identity")
  zph_full[[i]] <- res_full
}

zph_full[[rand]] #some non-proportionality of hazards for grisk, pirx, grade, her2
plot(res_full) #trend over time (not transformed); non-proportionality for above covariates not extreme
  
  rm(list=ls(pattern="^fit"))
  rm(list=ls(pattern="^zph"))
  rm(list=ls(pattern="^res"))
  rm(i)
  rm(dat)

#Observation of Schoenfeld residuals indicates that the proportional hazards assumption holds for MammaPrint/genomic risk and most covariates for prediction of breast cancer (BC) deaths. Although the BC-specific linear predictor, pirx, shows non-proportional behavior, the graphical analysis of residuals suggests the non-proportionality is not severe, also for: grade (effect goes up slightly over time, but in the first 5 years the change is minor), HER2 (effect goes up in the first 5 years and slowly goes down), and KI67 (effect attenuates after 10 years but seems more or less constant in the first 5 years).
```

# 6. Check linearity of continuous variables
```{r Lin}
# To assess linearity, we fit both a linear and non-linear term and check their significance.
dat_rand <- datapredimp_bc %>% filter(.imp==rand) #choose ith random imputed data
fit_pirx <- coxph(Surv(time, eventbc) ~ pspline(pirx), data = dat_rand) #if pspline df=0 is specified, pspline will choose the best df based on AIC
summary(fit_pirx) #non-linear term not necessary
  
fit_age <- coxph(Surv(time, eventbc) ~ offset(pirx) + pspline(age.start), data = dat_rand)
summary(fit_age) #non-linear term not necessary

fit_size <- coxph(Surv(time, eventbc) ~ offset(pirx) + pspline(size), data = dat_rand)
summary(fit_size) #non-linear term may be necessary

fit_nodes <- coxph(Surv(time, eventbc) ~ offset(pirx) + pspline(nodes), data = dat_rand)
summary(fit_nodes)#non-linear term not necessary

  rm(list = ls(pattern = "^fit"))
  rm(dat_rand, rand)
```

# 7. Check if necessary to adjust for country
```{r Country}
#Check addition of country as fixed effect
  fit_country1 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) + grisk))
  cbind(summary(pool(fit_country1))[,1], round(summary(pool(fit_country1))[,-1], 2))
  
  fit_country2 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) + grisk + country))
  cbind(summary(pool(fit_country2))[,1], round(summary(pool(fit_country2))[,-1], 2)) #effect of grisk not changed by country

  #check effect modification by country
  fit_country3 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) + grisk*country))
  cbind(summary(pool(fit_country3))[,1], round(summary(pool(fit_country3))[,-1], 2)) #with adjustment for original effects, interactions not significant (note: Slovenia and Switzerland have few observations)
  
  fit_country4 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*country))
  cbind(summary(pool(fit_country4))[,1], round(summary(pool(fit_country4))[,-1], 2)) #without adjustment for original effects, interactions also not significant

#Check addition of country as random effect
  fit_country5 <- imppred_bc %>% with(coxme(Surv(time, eventbc) ~ offset(pirx) + grisk + (1|country)))
  fit_country5$analyses
  
  #Fixed effects are interpreted as usual (effect of covariate on hazard rate), random effects accounts for variability at group level (here, between countries). The output for random effects includes a variance component that quantifies how much the hazard varies between levels of the random effect (countries). The variance component associated with countries is quite small suggesting not much variation in the hazard between countries (i.e., country-to-country variabiliy in survival outcome is minimal and the fixed effects explain most of the hazard variability)
  
#Check addition as a strata - necessary if baseline survival differs across countries
  for (i in 1:20) {
    dat <- datapredimp_bc %>%
      filter(.imp == i) %>%
      select(time, eventbc, pirx, country)
    
    dat$country2 <- ifelse(dat$country == "Slovenia" | dat$country == "Switzerland" | dat$country == "United Kingdom", "Others", as.character(dat$country)) #combine countries with few records
    dat$country2 <- as.factor(dat$country2)
    
    #Baseline survival estimates across countries, accounting for original effects from PREDICT
    fit_country6 <- coxph(Surv(time, eventbc) ~ offset(pirx) + strata(country2), data = dat)
    bsurv_estimates <- survfit(fit_country6)
    plot(bsurv_estimates, col = 1:length(unique(dat$country2)),
         xlab = "Time", ylab = "Survival Probability",
         lty = 1:length(unique(dat$country2)),
         ylim=c(0.9, 1.0))
    legend("bottomleft", legend = levels(dat$country2),
         col = 1:length(unique(dat$country2)),
         lty = 1:length(unique(dat$country2)))
  }
  
  #Baseline survival (cumhaz) is similar across countries, no need to add strata
    
  rm(list = ls(pattern = "^fit"))
  rm(bsurv_estimates)
  rm(plots)
  rm(dat, i)
```

# 8. Check effect modification of MammaPrint
```{r Independence}
#Check interactions with clinical risk factors
fit_pirx<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*pirx))
cbind(summary(pool(fit_pirx))[,1], round(summary(pool(fit_pirx))[,-1], 2)) #no significant interaction

fit_age<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*age.start))
cbind(summary(pool(fit_age))[,1], round(summary(pool(fit_age))[,-1], 2)) #no significant interaction

  ## By age category
  temp <- datapredimp_bc %>% mutate(agecat = ifelse(age.start >= 50, 1, 0))
  temp_mids <- as.mids(temp)
  fit_agecat<- temp_mids %>% with(coxph(Surv(time, eventbc) ~ grisk*agecat))
  cbind(summary(pool(fit_agecat))[,1], round(summary(pool(fit_agecat))[,-1], 2)) #no significant interaction
  
  temp_ge50 <- datapredimp_bc %>% filter(age.start >=50)
  temp_l50 <-datapredimp_bc %>% filter(age.start <50)
  temp_mids_ge50 <- as.mids(temp_ge50)
  temp_mids_l50 <- as.mids(temp_l50)
  
  fit_agecat<- temp_mids_ge50 %>% with(coxph(Surv(time, eventbc) ~ grisk))
  cbind(summary(pool(fit_agecat))[,1], round(summary(pool(fit_agecat))[,-1], 2))
  
  fit_agecat<- temp_mids_l50 %>% with(coxph(Surv(time, eventbc) ~ grisk))
  cbind(summary(pool(fit_agecat))[,1], round(summary(pool(fit_agecat))[,-1], 2))
  
  fit_agecat<- temp_mids_ge50 %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) + grisk))
  cbind(summary(pool(fit_agecat))[,1], round(summary(pool(fit_agecat))[,-1], 2))
  
  fit_agecat<- temp_mids_l50 %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) + grisk))
  cbind(summary(pool(fit_agecat))[,1], round(summary(pool(fit_agecat))[,-1], 2))

fit_size<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*size))
cbind(summary(pool(fit_size))[,1], round(summary(pool(fit_size))[,-1], 2)) #no significant interaction

fit_nodes<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*nodes))
cbind(summary(pool(fit_nodes))[,1], round(summary(pool(fit_nodes))[,-1], 2)) #no significant interaction

fit_grade<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*grade))
cbind(summary(pool(fit_grade))[,1], round(summary(pool(fit_grade))[,-1], 2)) #no significant interaction (P<0.05)

fit_her2<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*her2))
cbind(summary(pool(fit_her2))[,1], round(summary(pool(fit_her2))[,-1], 2)) #significant interaction, need to confirm in non-trial data

fit_her22<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) +  grisk*her2))
cbind(summary(pool(fit_her22))[,1], round(summary(pool(fit_her22))[,-1], 2)) #significant interaction remains after adjustment for effects of PREDICT

fit_her23<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + grisk*her2))
cbind(summary(pool(fit_her23))[,1], round(summary(pool(fit_her23))[,-1], 2)) #significant interaction remains after adjustment for effects of PREDICT

fit_her24<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) +  grisk + grisk:her2))
cbind(summary(pool(fit_her24))[,1], round(summary(pool(fit_her24))[,-1], 2)) #significant interaction remains after adjustment for effects of PREDICT

fit_ki67<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*ki67))
cbind(summary(pool(fit_ki67))[,1], round(summary(pool(fit_ki67))[,-1], 2)) #no significant interaction

fit_pr <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*pr))
cbind(summary(pool(fit_pr))[,1], round(summary(pool(fit_pr))[,-1], 2)) #no significant interaction

#Additional checks
fit_horm <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*horm))
cbind(summary(pool(fit_horm))[,1], round(summary(pool(fit_horm))[,-1], 2)) #significant interaction, need to confirm in non-trial data
##significant interaction

fit_chemo <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*generation))
cbind(summary(pool(fit_chemo))[,1], round(summary(pool(fit_chemo))[,-1], 2)) #no significant interaction

fit_traz <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*traz))
cbind(summary(pool(fit_traz))[,1], round(summary(pool(fit_traz))[,-1], 2)) #no significant interaction

fit_bis <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*bis))
cbind(summary(pool(fit_bis))[,1], round(summary(pool(fit_bis))[,-1], 2)) #no significant interaction

#The effect of MammaPrint (genomic risk) for breast cancer-specific mortality is largely independent of standard clinical risk factors except for HER2 status (perhaps sampling related, need to confirm with registry data). We retained the simple extended models without interactions for now. Note that we did not check genomic risk interaction with ER status as we restricted the analyses to only ER+ tumors. If we used the overall dataset, it still would not have been possible to obtain the interaction effect of genomic risk with ER status as there were zero events in the genomic low risk subgroup of ER- tumors.

  rm(list = ls(pattern = "^fit"))
  rm(list = ls(pattern = "^temp"))
```

```{r Save}
#save.image("WS_1_Data_Prep_MINDACT.RData")
```

