---
title: 'Preparing the MINDACT dataset'
author: 'Mary Ann Binuya'
date: '2024-02-27'
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

```{r setup, include=FALSE}
#Set libpath
#.libPaths(c('U:/libraries', .libPaths()))

knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = FALSE,
  fig.retina = 3,
  fig.path = 'Output/1 Data Prep/')

#Load libraries
library(survival) #for data splitting
library(dplyr) #for data manipulations
library(mice) #for imputations
library(cmprsk) #for competing risk analysis
library(riskRegression) #for fgr 
library(cmprsk) #for fgr
library(lava) #for fgr
library(prodlim) #for fgr
library(survminer) #for ggsurvplot
library(coxme) #for mixed effect Cox model

rm(list=ls())
```

# Aim(s)
1. To import and prepare MINDACT dataset
2. To create imputed MINDACT dataset(s)
3. To run PREDICT on imputed MINDACT dataset(s)
4. To check significance of genomic risk for predicting competing events (breast cancer and other deaths)
5. To check proportionality of hazards
6. To check linearity of continuous variables
7. To check if it is necessary to adjust for country
8. To check if genomic risk effect is modified by other risk factors

# 1. Import and prepare dataset
```{r Prep}
# Load data
  mindact <- readxl::read_excel('Data/10041_MIND001_002_transfer.xlsx')
 
  data <- mindact %>%
    select(patid_rand, #Patient IDs to check number of unique records
           tables_AP2,#Group: corrected risk
           Country, #Country, for sensitivity analysis
           clinical_risk, #Adjuvant! Online risk (uncorrected)
           clinical_risk_crg, #Adjuvant! Online risk (corrected)
           genomic_risk, #Genomic risk (uncorrected)
           genomic_risk_crg, #Genomic risk (corrected)
           age, #Age at diagnosis
           meno_MV, #Menopausal status
           tsizecrg, #Tumor size in mm
           tgradpr, tgradelcrg, #Histological grade central and local
           lnstatuscrg, #Number of positive nodes
           er_strict, erstatcrg, #ER status central and local
           pgr_strict, pgrstatcrg, #PR status central and local
           her_bin, her2_local, #Her2 central and local
           ki67_3, #Ki67 status
           chemo_trt2, #Chemotherapy
           adj_ht, #Hormone therapy
           adj_tras, #Anti-HER2 therapy
           OS, OS_CR, OStime) %>% #Overall survival, Overall survival (competing risk), Follow-up time
   rename(pid = patid_rand,
          rgroup = tables_AP2,
          country=Country,
          crisk_ao=clinical_risk_crg,
          grisk=genomic_risk_crg,
          age.start=age,
          menop=meno_MV,
          size=tsizecrg,
          grade_central=tgradpr,
          grade_local=tgradelcrg,
          nodes=lnstatuscrg,
          er_central=er_strict,
          er_local=erstatcrg,
          pr_central=pgr_strict,
          pr_local=pgrstatcrg,
          her2_central=her_bin,
          ki67=ki67_3,
          chemo=chemo_trt2,
          horm=adj_ht,
          traz=adj_tras,
          os=OS,
          oscr=OS_CR,
          time=OStime) %>%
    mutate(eventbc = ifelse(oscr==1, 1, 0), #BC events
           eventoth = ifelse(oscr==2, 1, 0)) #Other events

# Explore data
  n_distinct(data$pid) #6693 unique IDs/patients
  
  #country
  table(data$country, useNA='always') #no missing
  
  #age
  data$age.start <- round(data$age.start,0)
  table(data$age.start, useNA='always') #no missing; 3 patients outside of PREDICT recommended range (25-85) but close enough so retain
  
  #menopausal status (relevant for bisphosphonates use)
  table(data$menop, useNA='always') #251 missing
  
  #size in mm
  table(data$size, useNA='always') #no missing but 1 patient with size=0, confirmed DCIS; exclude
  
    data$er_local[data$size=='0'] #patient with size=0 is ER+, which will cause the breast cancer specific linear predictor of PREDICT to be -Inf; exclude
    
  #grade - use central lab, otherwise (if missing) use local to be consistent with previous MINDACT analysis
  data$grade <- ifelse(!is.na(data$grade_central), data$grade_central, data$grade_local)
  table(data$grade, useNA='always') #11 missing, recode as NA
  data$grade[data$grade==9] <- NA
  
  #nodes - note: category 4 is 4+ nodes
  table(data$nodes, useNA='always') #1 missing
  
  #er status - use central lab, otherwise (if missing) use local
  data$er <- ifelse(!is.na(data$er_central), data$er_central, data$er_local) #1% cut-off per protocol
  table(data$er, useNA='always') #no missing
  
  #pr status - use central lab, otherwise (if missing) use local
  data$pr <- ifelse(!is.na(data$pr_central), data$pr_central, data$pr_local) #1% cut-off per protocol
  table(data$pr, data$er, useNA='always') #1 missing (ER+)
  
  #her2 status - use central lab, otherwise (if missing) use local
  data$her2 <- ifelse(!is.na(data$her2_central), data$her2_central, data$her2_local)
  table(data$her2, useNA='always') #2 missing
  
  #ki67 status - note: cut-offs are 14%, 20%% (PREDICT uses cut off of 10%)
  data$ki67[data$ki67==2] <- 1 #combine levels above 14%
  table(data$ki67, useNA='always') #841 missing
  
  #chemotherapy generation
  data$generation <- ifelse(data$chemo==3|data$chemo==4, 3, data$chemo) #taxane-based regimens
  data$generation[data$chemo==5] <- NA #recode other/unknown to NAs
  table(data$generation, useNA='always') #220 missing chemo; exclude 9 patients treated with first generation chemo as PREDICT doesn't allow this; moreover, missing patients are unlikely to be treated with first gen (year of diagnosis: 2007-11; while around 2001 taxanes (3rd gen) were already available for treatment of advanced breast cancer)

  #hormone therapy
  table(data$horm, useNA='always') #117 missing
  
  #anti-HER2/trastuzumab therapy
  table(data$traz, useNA='always') #112 missing
  
  #crisk
  table(data$crisk_ao, useNA='always') #1 missing
  data$crisk_ao[is.na(data$crisk_ao)] <- 0 #recode to low per MINDACT codebook
  
  #grisk
  table(data$grisk, useNA='always') #1 missing
  data$grisk[is.na(data$grisk)] <- 0 #recode to low per MINDACT codebook
  
    #noted: 176 (2.6%) discrepancies between corrected and uncorrected grisk --> use corrected risks
    table(data$grisk, data$genomic_risk, useNA='always')
  
  #follow-up time
  data$time <- round(data$time/365.25,2) #convert days to years
  data$time <- ifelse(data$time == 0, 0.003, data$time) #2 patients with time=0 years actually died after 1 day, corrected
    
# Create the variables needed in PREDICT but not available in MINDACT
  #method of screening
  data$screen <- 2 #assume unknown for all
  
  #bisphophonates
  data$bis <- NA
  data$bis <- ifelse(data$menop==2, 1, ifelse(data$menop==1, 0, data$bis)) #assume post-menopausal women received bisphosphonates
  data$bis[is.na(data$bis)&data$age.start>50] <- 1 #use 50 as age cut off for menopause
  data$bis[is.na(data$bis)&data$age.start<=50] <- 0
  table(data$bis, useNA='always')

# Retain only eligible records per above
  dataelig <- data %>%
    filter(size > 0, #exclude 1 DCIS patient with size=0
           generation != 1 | is.na(generation)) #exclude 9 patients treated with first generation chemo
  
# Retain only variables relevant for subsequent analysis
  dataimp <- dataelig %>%
    filter (er == 1) %>% #limit to ER+ patients
    select(country, grisk, age.start, screen, size, grade, nodes, er, pr, her2, ki67,
           generation, horm, traz, bis, os, oscr, time, eventbc, eventoth)
```

# 2. Create imputed dataset(s)
```{r Imp}
# Check missingness pattern
  md.pattern(dataimp, rotate.names = TRUE) #assume MAR

# Reformat variables
  dataimp[, c('country', 'grisk', 'er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')] <- lapply(dataimp[, c('country', 'grisk', 'er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')], FUN=as.factor) #you can also use unclass() and assign class per variable but this is faster

# Calculate marginal baseline cumhaz
  dataimp$cumhaz_bc <- nelsonaalen(dataimp, time, eventbc)
  dataimp$cumhaz_oth <- nelsonaalen(dataimp, time, eventoth)

# Imputation
  ini <- mice(dataimp, maxit=0)
  ini$nmis #number of missing per variable
  
  vis <- c('nodes', 'pr', 'her2', 'grade', 'traz', 'horm', 'generation', 'ki67') #define order of imputation; alternatively, you can also just manually change the order of the columns
  
  method <- ini$method #check appropriate methods are used per variable
  method
  
  pred_bc <- ini$predictorMatrix
  pred_bc[,'screen'] <- 0 #exclude, constant
  pred_bc[,'bis'] <- 0 #exclude, derived variable
  pred_bc[,'os'] <- 0
  pred_bc[,'oscr'] <- 0
  pred_bc[,'eventoth'] <- 0
  pred_bc[,'cumhaz_oth'] <- 0
  pred_bc #keep as predictors: survival time, status indicator, baseline cumhaz, and relevant covariates

  
  pred_oth <- ini$predictorMatrix
  pred_oth[,'screen'] <- 0 #exclude, constant
  pred_oth[,'bis'] <- 0 #exclude, derived variable
  pred_oth[,'os'] <- 0
  pred_oth[,'oscr'] <- 0
  pred_oth[,'eventbc'] <- 0
  pred_oth[,'cumhaz_bc'] <- 0
  pred_oth #keep as predictors survival time, status indicator, baseline cumhaz, and relevant covariates

# Impute separately for each competing event
  
  #Breast cancer deaths
  imp_bc <- mice(dataimp, m=20, visitSequence = vis, method=method, predictorMatrix=pred_bc, seed=202309) #FMI~0.2=20 imputations (see White, Royston, Wood, 2011)
    
  sapply(complete(imp_bc), function(x) sum(is.na(x))) #check no more missing
  plot(imp_bc) #check convergence is ok
  densityplot(imp_bc, ~grade+ki67+generation+horm+traz) #check distribution of original (blue) and imputed (red) data; note nodes, her2, and pr not in plot (only one missing each); also note levels are not correctly presented (this is not an error in imputed values, it's just the way MICE creates labels).
  
  imp_oth <- mice(dataimp, m=20, visitSequence = vis, method=method, predictorMatrix=pred_oth, seed=202309)
  
  #Other deaths
  sapply(complete(imp_oth), function(x) sum(is.na(x)))
  plot(imp_oth)
  densityplot(imp_oth, ~grade+ki67+generation+horm+traz)

  rm(ini, pred_bc, pred_oth, method, vis)
```

# 3. Run PREDICT on imputed dataset(s)
```{r PREDICT}
# Load PREDICT version 2.3 function
source('Functions/predictv23_batchrunner.R')

# Run PREDICT on imp_bc
  datapredimp_bc <- complete(imp_bc, action='long', include=TRUE) #complete imputed data

  datapredimp_bc[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')] <- as.numeric(as.matrix(datapredimp_bc[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')])) #format variables for PREDICT function
  
  datapredimp_bc <- ukpredict(datapredimp_bc, year=5, age.start=age.start, screen=screen, size=size, grade=grade, nodes=nodes, er=er, pr=pr, her2=her2, ki67=ki67, generation=generation, horm=horm, traz=traz, bis=bis)
  
  datapredimp_bc[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')] <- lapply(datapredimp_bc[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')], FUN=as.factor) #format variables back
  
  imppred_bc <- as.mids(datapredimp_bc)
  
# Run PREDICT on imp_oth
  datapredimp_oth <- complete(imp_oth, action='long', include=TRUE) #complete imputed data
  
  datapredimp_oth[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')] <- as.numeric(as.matrix(datapredimp_oth[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')])) #format variables for PREDICT function
  
  datapredimp_oth <- ukpredict(datapredimp_oth, year=5, age.start=age.start, screen=screen, size=size, grade=grade, nodes=nodes, er=er, pr=pr, her2=her2, ki67=ki67, generation=generation, horm=horm, traz=traz, bis=bis)
  
  datapredimp_oth[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')] <- lapply(datapredimp_oth[, c('er', 'pr', 'her2', 'ki67', 'generation', 'horm', 'traz', 'bis')], FUN=as.factor) #format variables back
  
  imppred_oth <- as.mids(datapredimp_oth)

  rm(list=setdiff(ls(), c('datapredimp_bc', 'datapredimp_oth', 'imppred_bc', 'imppred_oth')))
```

# 4. Check significance of genomic risk for predicting competing events
```{r Outcomes}
# PREDICT considers two competing events in predicting overall mortality: breast cancer death and other/unknown deaths. We check if MammaPrint is a significant predictor for both events.

  #Breast cancer
    fit_bcss <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk))
    summary(pool(fit_bcss)) #grisk/MammaPrint a significant predictor for breast cancer death

    fit_bcss_m <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + grisk))
    summary(pool(fit_bcss_m)) #grisk/MammaPrint a significant predictor for breast cancer death
    
  #Other
    fit_oth <- imppred_oth %>% with(coxph(Surv(time, eventoth) ~ grisk))
    summary(pool(fit_oth)) #grisk/MammaPrint not a significant predictor for other/unknown death
    
    fit_oth_m <- imppred_oth %>% with(coxph(Surv(time, eventoth) ~ mi + grisk))
    summary(pool(fit_oth_m)) #grisk/MammaPrint not a significant predictor for other/unknown death
    
    rm(list=ls(pattern="^fit"))
  
# Let's do a sanity check using subdistribution hazard models instead of cause-specific models
  #Breast cancer
    fgr_res <- fgr_res_m <- list()

    for (i in 1:20) {
      df <- datapredimp_bc %>% filter(.imp == i)
      fgr_bcss <- FGR(Hist(time, oscr) ~ grisk, cause = 1, data = df)
      fgr_res[[i]] <- summary(fgr_bcss)$coef
      
      fgr_bcss_m <- FGR(Hist(time, oscr) ~ pirx + grisk, cause = 1, data = df)
      fgr_res_m[[i]] <- summary(fgr_bcss_m)$coef
    }
    
    fgr_res #similar results as cause-specific model likely due to low event rates
    fgr_res_m #similar results as cause-specific model likely due to low event rates
    
    rm(list=ls(pattern="^fgr"))
    
  #Other - subdistribution models
    fgr_res <- fgr_res_m <- list()

    for (i in 1:20) {
      df <- datapredimp_bc %>% filter(.imp == i)
      fgr_oths <- FGR(Hist(time, oscr) ~ grisk, cause = 2, data = df)
      fgr_res[[i]] <- summary(fgr_oths)$coef
      
      fgr_oths_m <- FGR(Hist(time, oscr) ~ mi + grisk, cause = 2, data = df)
      fgr_res_m[[i]] <- summary(fgr_oths_m)$coef
    }
    
    fgr_res #similar results as cause-specific model
    fgr_res_m #similar results as cause-specific model
    
    rm(list=ls(pattern="^fgr"))
    rm(df)
    
# Limit analysis to prediction of breast cancer deaths.
```

# 5. Check proportionality of hazards
```{r PH}
zph <- zph_full <- list()

for (i in 1:20) {
  dat <- datapredimp_bc %>%
    filter(.imp == i) %>%
    select(time, eventbc,
           grisk, pirx, age.start, size, grade, nodes, pr, her2, ki67, generation, horm, traz, bis)
  
  fit_bc <- coxph(Surv(time, eventbc) ~ grisk, data = dat)
  res <- cox.zph(fit_bc, transform = 'identity')
  zph[[i]] <- res
  
  fit_bc_full <- coxph(Surv(time, eventbc) ~ ., data = dat) #include all covariates
  res_full <- cox.zph(fit_bc_full, transform = 'identity')
  zph_full[[i]] <- res_full
}

rand <- sample(1:20, 1) #show result only of the ith random imputed data (results almost identical across imputed datasets)

zph[[rand]] #grisk hazard is reasonably proportional over time
zph_full[[rand]] #pirx, grade, her2, and ki67 do not have proportional hazards according to individual test
plot(res_full) #trend over time (not transformed); non-proportionality for above covariates not extreme
  
  rm(list=ls(pattern="^fit"))
  rm(list=ls(pattern="^zph"))
  rm(list=ls(pattern="^res"))
  rm(i, rand)
  rm(dat)

#The Schoenfeld residuals test indicates that the proportional hazards assumption is generally upheld for MammaPrint/genomic risk and most covariates for prediction of breast cancer (BC) deaths. Although the BC-specific linear predictor, pirx, shows non-proportional behavior, the graphical analysis of residuals suggests the non-proportionality is not that severe, also for the following covariates: Grade effect goes up slightly over time (in the first 5 years the change is minor). HER2 effect goes up in the first 5 years and slowly goes down, and KI67 effect attenuates after 10 years but seems more or less constant in the first 5 years.
```

# 6. Check linearity of continuous variables
```{r Lin}
# To assess linearity, we fit both a linear and non-linear term and check their significance.

fit_pirx <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pspline(pirx))) #if df=0 is specified, pspline will choose the best df based on AIC
fit_pirx_res <- summary(fit_pirx)
mean(fit_pirx_res$p.value[fit_pirx_res$term == 'pspline(pirx), nonlin']) #mean p-val for non-linear term > 0.05; linear enough
  
fit_age <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + pspline(age.start)))
fit_age_res <- summary(fit_age)
mean(fit_age_res$p.value[fit_age_res$term == 'pspline(age.start), nonli']) #linear
  
fit_size <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + pspline(size)))
fit_size_res <- summary(fit_size)
mean(fit_size_res$p.value[fit_size_res$term == 'pspline(size), nonlin'])  #size is non-linear, addition of this term --> more tailored model to MINDACT

fit_nodes <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + pspline(nodes)))
fit_nodes_res <- summary(fit_nodes)
mean(fit_nodes_res$p.value[fit_nodes_res$term == 'pspline(nodes), nonlin']) #linear
mean(fit_nodes_res$p.value[seq(3, nrow(fit_nodes_res), by = 3)])  #linear

  rm(list = ls(pattern = '^fit'))
```

# 7. Check if necessary to adjust for country
```{r Country}
#Check as fixed effect
  fit_country1 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + grisk))
  cbind(summary(pool(fit_country1))[,1], round(summary(pool(fit_country1))[,-1], 2))
  
  fit_country2 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + grisk + country))
  cbind(summary(pool(fit_country2))[,1], round(summary(pool(fit_country2))[,-1], 2)) #effect of grisk not confounded by country
  
  fit_country3 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx + grisk*country))
  cbind(summary(pool(fit_country3))[,1], round(summary(pool(fit_country3))[,-1], 2)) #interactions not significant (note: Slovenia and Switzerland have few observations), controlling for clinical risk
  
  fit_country4 <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*country))
  cbind(summary(pool(fit_country4))[,1], round(summary(pool(fit_country4))[,-1], 2)) #interactions not significant (note: Slovenia and Switzerland have few observations), not controlling for clinical risk

#Check as random effect
  fit_country5 <- imppred_bc %>% with(coxme(Surv(time, eventbc) ~ pirx + grisk + (1|country)))
  fit_country5
  
  #The fixed effects are interpreted as usual; the random effects indicate how much variation is present between the levels of the random effect variable (e.g., between countries). Here we can see that the variance component associated with the random effect is quite small (there is not much variation between countries).
  
  #The addition of country as fixed or random effect did not impact the predictor effects for pirx and grisk (i.e., their effects are independent of country).

#Check baseline differences across countries
  for (i in 1:20) {
    dat <- datapredimp_bc %>%
      filter(.imp == i) %>%
      select(time, eventbc, pirx, country)
    
    dat$country2 <- ifelse(dat$country == "Slovenia" | dat$country == "Switzerland" | dat$country == "United Kingdom", "Others", as.character(dat$country))
    dat$country2 <- as.factor(dat$country2)
    
    #Baseline survival across countries with linear predictor offset
    fit_country5 <- coxph(Surv(time, eventbc) ~ offset(pirx) + strata(country2), data = dat)
    surv_estimates <- survfit(fit_country5)
    plot(surv_estimates, col = 1:length(unique(dat$country2)),
         xlab = "Time", ylab = "Survival Probability",
         lty = 1:length(unique(dat$country2)),
         ylim=c(0.9, 1.0))
    legend("bottomleft", legend = levels(dat$country2),
         col = 1:length(unique(dat$country2)),
         lty = 1:length(unique(dat$country2)))
    
    #Baseline cumulative hazard across countries (based on Kaplan-Meier estimates)
    fit_country6 <- survfit(Surv(time, eventbc) ~ country2, data = dat)
    
    plots<- ggsurvplot(fit_country6, pval = TRUE, data=dat, conf.int = FALSE,
                   title = "Cumulative hazard",
                   xlab = "Years", fun="cumhaz",
                   ylim=c(0,0.15), risk.table = FALSE)
    
    print(plots)
  }
  
  #Baseline cumulative survival (hazard) across countries is largely similar
    
  rm(list = ls(pattern = '^fit'))
  rm(surv_estimates)
  rm(plots)
  rm(dat, i)
```

# 8. Check effect modification
```{r Independence}
#Check interactions with clinical risk factors
fit_pirx<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*pirx))
cbind(summary(pool(fit_pirx))[,1], round(summary(pool(fit_pirx))[,-1], 2))

fit_age<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*age.start))
cbind(summary(pool(fit_age))[,1], round(summary(pool(fit_age))[,-1], 2))

fit_size<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*size))
cbind(summary(pool(fit_size))[,1], round(summary(pool(fit_size))[,-1], 2))

fit_nodes<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*nodes))
cbind(summary(pool(fit_nodes))[,1], round(summary(pool(fit_nodes))[,-1], 2))

fit_grade<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*grade))
cbind(summary(pool(fit_grade))[,1], round(summary(pool(fit_grade))[,-1], 2))

fit_her2<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*her2))
cbind(summary(pool(fit_her2))[,1], round(summary(pool(fit_her2))[,-1], 2))
##significant interaction, effect modified (increased)

fit_her22<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) +  grisk*her2))
cbind(summary(pool(fit_her22))[,1], round(summary(pool(fit_her22))[,-1], 2))

fit_her23<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ pirx +  grisk*her2))
cbind(summary(pool(fit_her23))[,1], round(summary(pool(fit_her23))[,-1], 2))

fit_her24<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ offset(pirx) +  grisk + grisk:her2))
cbind(summary(pool(fit_her24))[,1], round(summary(pool(fit_her24))[,-1], 2))

fit_ki67<- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*ki67))
cbind(summary(pool(fit_ki67))[,1], round(summary(pool(fit_ki67))[,-1], 2))

fit_pr <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*pr))
cbind(summary(pool(fit_pr))[,1], round(summary(pool(fit_pr))[,-1], 2))

#Additional checks
fit_horm <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*horm))
cbind(summary(pool(fit_horm))[,1], round(summary(pool(fit_horm))[,-1], 2))
##significant interaction

fit_chemo <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*generation))
cbind(summary(pool(fit_chemo))[,1], round(summary(pool(fit_chemo))[,-1], 2))

fit_traz <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*traz))
cbind(summary(pool(fit_traz))[,1], round(summary(pool(fit_traz))[,-1], 2))

fit_bis <- imppred_bc %>% with(coxph(Surv(time, eventbc) ~ grisk*bis))
cbind(summary(pool(fit_bis))[,1], round(summary(pool(fit_bis))[,-1], 2))

#The prognostic effect of genomic risk for breast cancer-specific mortality is largely independent of standard clinical risk factors except for HER2 status (likely sampling related). We retained the simple extended models without interactions for parsimony.

#Note that we did not check genomic risk interaction with ER status as we restricted the analyses to only ER+ tumors. If we used the overall dataset, it still would not have been possible to obtain the interaction effect of genomic risk with ER status as there were zero events in the genomic low risk subgroup of ER- tumors.

  rm(list = ls(pattern = '^fit'))
```

```{r Save}
#save.image('WS_1_Data_Prep_MINDACT.RData')
```

