---
title: "Updating and extension of PREDICT using MINDACT - continued"
author: "Mary Ann Binuya"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document: default
---

# Aim
1. To check the performance of the following updated/extended models:\
&emsp;Method 1. Model with recalibration-in-the-large (only baseline is re-estimated)\
&emsp;Method 2. Recalibrated model (both baseline and slope are re-estimated)\
&emsp;Method 3. Revised model (additional regression coefficients are added)\
&emsp;Method 3. Revised model (LASSO)\

```{r setup, include=FALSE}
#Set libpath
#.libPaths(c("U:/libraries", .libPaths()))

knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = FALSE,
  fig.retina = 4,
  fig.path = "Output/4 Extension - Val plots and DCA/")

#Load libraries
library(dplyr) #for data manipulations
library(survival) #for survival analysis
library(rms) #for survival analysis
library(glmnet) #supports survival models
library(caret) #doesn'"'t support survival models
library(writexl) #for exporting datasets
library(ggpubr) #for arranging plots
```

# Load data
```{r Load}
# Load data and results of original model"s external validation
  load("WS_4_PREDICT_extension.RData")
```

# LRT
```{r LRT}
#Method1:
pool_lrt(data = dat, impvar=".imp", nimp = 20,
         formula = form1g,
         nullformula = form1)

#Method2:
pool_lrt(data = dat, impvar=".imp", nimp = 20,
         formula = form2g,
         nullformula = form2)

#Method3: Full revision:
formfull <- Surv(time, eventbc) ~ pirx + age.start + size + grade + nodes + pr +
                                  her2 + ki67 + generation + horm + traz + bis
formfullg <- Surv(time, eventbc) ~ pirx + grisk + age.start + size + grade + nodes + pr +
                                  her2 + ki67 + generation + horm + traz + bis
pool_lrt(data = dat, impvar=".imp", nimp = 20,
         formula = formfullg,
         nullformula = formfull)

#Method3: LASSO --> do not report
  #LL without grisk
    covariates <- dat %>% select(pirx, age.start, size, grade, nodes, pr, her2, ki67,
                 generation, horm, traz, bis)
    X <- model.matrix( ~ ., covariates)[, -1]
    Y <- cbind(time = dat$time, status = dat$eventbc)
    df <- data.frame(Y, X)
    
    model_rev <- glmnet(X, Y, family = "cox", lambda = 0) #no penalization
    model_null <- coxph(Surv(time, status) ~ 1, data = df)
    ll_null <- model_null$loglik
    ll_sat <- model_rev$nulldev / 2 + ll_null
    ll_rev <- ll_sat - deviance(model_rev) / 2
    df_rev <- length(coef(model_rev, s = 0)@x)
  
  #LL with grisk
    covariates_g <- dat  %>% select(pirx, grisk, age.start, size, grade, nodes, pr, her2, ki67,
                 generation, horm, traz, bis)
    X_g <- model.matrix( ~ ., covariates_g)[, -1]
    df_g <- data.frame(Y, X_g)
    
    model_rev_g <- glmnet(X_g, Y, family = "cox", lambda = 0) #no penalization
    model_null <- coxph(Surv(time, status) ~ 1, data = df)
    ll_null <- model_null$loglik
    ll_sat_g <- model_rev_g$nulldev / 2 + ll_null
    ll_rev_g <- ll_sat_g - deviance(model_rev_g) / 2
    df_rev_g <- length(coef(model_rev_g, s = 0)@x)
    
  #LRT (non-penalized LASSO models):
    dev <- 2*(ll_rev_g - ll_rev)
    pval <- (1 - pchisq(dev, df_rev_g-df_rev))
    cbind(dev, pval)
```

# Calibration plots
```{r Valplots, fig.height=5, fig.width=5}
calplot2df_C <- function(data1, data2, tmax, main, limit, size_lab = 1, size_legend = 0.5, triangles = FALSE, g, Cdif){
  #data1 = risk_df file without grisk
  #data2 = risk_df file with grisk

  # Predicted risks for data1
  data1$x1 <- data1$predicted_risk
  data1$x1.ll <- log(-log(1 - data1$x1))
  
  # Predicted risks for data2
  data2$x2 <- data2$predicted_risk
  data2$x2.ll <- log(-log(1 - data2$x2))
  
  model1 <- cph(Surv(time, event) ~ rcs(x1.ll, 5), data = data1, x = TRUE, y = TRUE, surv = TRUE)
  model2 <- cph(Surv(time, event) ~ rcs(x2.ll, 5), data = data2, x = TRUE, y = TRUE, surv = TRUE)
  
  # Observed risks for data1
  xx1 <- seq(quantile(data1$x1, prob = 0.01), quantile(data1$x1, prob = 0.99), length = 100)
  xx1.ll <- log(-log(1 - xx1))
  xx1.ll.df <- data.frame(x1.ll = xx1.ll)
  y1 <- 1 - survest(model1, newdata = xx1.ll.df, times = tmax)$surv
  y1.lower <- 1 - survest(model1, newdata = xx1.ll.df, times = tmax)$upper
  y1.upper <- 1 - survest(model1, newdata = xx1.ll.df, times = tmax)$lower
  
  # Observed risks for data2
  xx2 <- seq(quantile(data2$x2, prob = 0.01), quantile(data2$x2, prob = 0.99), length = 100)
  xx2.ll <- log(-log(1 - xx2))
  xx2.ll.df <- data.frame(x2.ll = xx2.ll)
  y2 <- 1 - survest(model2, newdata = xx2.ll.df, times = tmax)$surv
  y2.lower <- 1 - survest(model2, newdata = xx2.ll.df, times = tmax)$upper
  y2.upper <- 1 - survest(model2, newdata = xx2.ll.df, times = tmax)$lower
  
  # Plot parameters
  xlim <- c(0, limit+0.01)
  ylim <- c(0, limit+0.01)
  xlab <- "Predicted probability"
  ylab <- "Observed proportion"
  
  # Plot
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(0, 0, type = "n",
       xlim = xlim, ylim = ylim,
       xlab = xlab, ylab = ylab,
       main = main, cex.main = 1,
       cex.lab = size_lab, cex.axis = size_lab, lwd = 2)
  polygon(c(xx1, rev(xx1), xx1[1]),
          c(y1.lower, rev(y1.upper), y1.lower[1]),
          border = NA, density = 50, angle = -20, col = "light gray")
  polygon(c(xx2, rev(xx2), xx2[1]),
          c(y2.lower, rev(y2.upper), y2.lower[1]),
          border = NA, density = 50, angle = 20, col = "light gray")
  abline(coef = c(0, 1), lty = 1, col = "gray") #diagonal line
  lines(xx1, y1, lwd = 2, col = "black")
  lines(xx2, y2, lty = 2, lwd = 2, col = "black")  # Add a second line (data2) in blue
  
  # Triangles
  if (triangles) {
    q1 <- Hmisc::cut2(data1$x1, levels.mean = TRUE, g = g)
    q2 <- Hmisc::cut2(data2$x2, levels.mean = TRUE, g = g)
    means1 <- as.double(levels(q1))
    means2 <- as.double(levels(q2))
    y1 <- 1-survest(model1, newdata=data1, times = tmax)$surv
    y2 <- 1-survest(model2, newdata=data2, times = tmax)$surv
    prop1 <- tapply(y1, q1, mean)
    prop2 <- tapply(y2, q2, mean)
    points(means1, prop1, pch = 17, cex = 1, col = "black")
    points(means2, prop2, pch = 17, cex = 1, col = "black")
  }
  
  # Legend
  legend("topleft", legend = c("Model without MammaPrint", "Model with MammaPrint"),
         col = c("black", "black"), lty = c(1, 2), lwd = 2, cex = size_legend, bty = "n")
  
  # Text
  text(x=limit-0.03, y=0.005, labels=paste("C difference: ", Cdif, sep=""), cex=0.8, pos=4)
}

# Method 1:
calplot2df_C(data1 = form1_riskdf,
        data2 = form1g_riskdf,
        tmax = 5,
        main = "Recalibration-in-the-large",
        limit = 0.1,
        size_lab = 0.75,
        size_legend = 0.75,
        triangles = FALSE,
        g = 5,
        Cdif = "0.03")

# Method 2:
calplot2df_C(data1 = form2_riskdf,
        data2 = form2g_riskdf,
        tmax = 5,
        main = "Recalibration",
        limit = 0.1,
        size_lab = 0.75,
        size_legend = 0.75,
        triangles = FALSE,
        g = 5,
        Cdif = "0.03")

# Method 3 (backward selection with shrinkage)
calplot2df_C(data1 = form3_riskdf,
        data2 = form3g_riskdf,
        tmax = 5,
        main = "Revision (backward selection with shrinkage)",
        limit = 0.1,
        size_lab = 0.75,
        size_legend = 0.75,
        triangles = FALSE,
        g = 5,
        Cdif = "0.02")

# Method 3 (LASSO): training dataset
calplot2df_C(data1 = form4train_riskdf,
        data2 = form4gtrain_riskdf,
        tmax = 5,
        main = "Revision (LASSO) - training dataset",
        limit = 0.1,
        size_lab = 0.75,
        size_legend = 0.75,
        triangles = FALSE,
        g = 5,
        Cdif = "0.02")

# Method 3 (LASSO): test dataset
calplot2df_C(data1 = form4test_riskdf,
        data2 = form4gtest_riskdf,
        tmax = 5,
        main = "Revision (LASSO) - test dataset",
        limit = 0.1,
        size_lab = 0.75,
        size_legend = 0.75,
        triangles = FALSE,
        g = 5,
        Cdif = "0.02")
```

# Decision curves
```{r DCA_plots, fig.height=5, fig.width=7}
# Method 1
  eventrate = 1 - summary(survfit(Surv(time, event) ~ 1, data = form0_riskdf), times = tmax)$surv
  
  #Net TP
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TP$threshold,
       form0_nb_TP$NB_all*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 5), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TP$threshold, form0_nb_TP$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TP$threshold, form1_nb_TP$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 1 without grisk
  smooth2 <- smooth.spline(form0_nb_TP$threshold, form1g_nb_TP$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 1 with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  abline(v=eventrate, col="black", lty=2)
  legend("topright", legend = c("Treat all", "Original model", "Recalibration-in-the-large", "Recalibration-in-the-large with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
  
  #Net TN
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TN$threshold,
       form0_nb_TN$NB_none*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 1000), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TN$threshold, form0_nb_TN$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TN$threshold, form1_nb_TN$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 1 without grisk
  smooth2 <- smooth.spline(form0_nb_TN$threshold, form1g_nb_TN$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 1 with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  legend("bottomright", legend = c("Treat none", "Original model", "Recalibration-in-the-large", "Recalibration-in-the-large with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
  
# Method 2
  #Net TP
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TP$threshold,
       form0_nb_TP$NB_all*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 5), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TP$threshold, form0_nb_TP$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TP$threshold, form2_nb_TP$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 2 without grisk
  smooth2 <- smooth.spline(form0_nb_TP$threshold, form2g_nb_TP$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 2 with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  abline(v=eventrate, col="black", lty=2)
  legend("topright", legend = c("Treat all", "Original model", "Recalibration", "Recalibration with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
  
  #Net TN
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TN$threshold,
       form0_nb_TN$NB_none*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 1000), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TN$threshold, form0_nb_TN$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TN$threshold, form2_nb_TN$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 2 without grisk
  smooth2 <- smooth.spline(form0_nb_TN$threshold, form2g_nb_TN$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 2 with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  legend("bottomright", legend = c("Treat none", "Original model", "Recalibration", "Recalibration with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))

# Method 3 - Revision (backward selection with shrinkage)
  #Net TP
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TP$threshold,
       form0_nb_TP$NB_all*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 5), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TP$threshold, form0_nb_TP$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TP$threshold, form3_nb_TP$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 3 without grisk
  smooth2 <- smooth.spline(form0_nb_TP$threshold, form3g_nb_TP$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 3 with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  abline(v=eventrate, col="black", lty=2)
  legend("topright", legend = c("Treat all", "Original model", "Model revision", "Model revision with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
  
  #Net TN
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TN$threshold,
       form0_nb_TN$NB_none*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 1000), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TN$threshold, form0_nb_TN$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TN$threshold, form3_nb_TN$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 3 (backward with shrinkage) without grisk
  smooth2 <- smooth.spline(form0_nb_TN$threshold, form3g_nb_TN$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 3 (backward with shrinkage) with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  legend("bottomright", legend = c("Treat none", "Original model", "Model revision", "Model revision with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))

# Method 3 - LASSO (train dataset)
  #Net TP
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TP$threshold,
       form0_nb_TP$NB_all*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 5), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TP$threshold, form0_nb_TP$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TP$threshold, form4train_nb_TP$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 3 (LASSO - train) without grisk
  smooth2 <- smooth.spline(form0_nb_TP$threshold, form4gtrain_nb_TP$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 3 (LASSO - train) with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  abline(v=eventrate, col="black", lty=2)
  legend("topright", legend = c("Treat all", "Original model", "Model revision (LASSO - train)", "Model revision with MammaPrint (LASSO - train)"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
  
  #Net TN
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TN$threshold,
       form0_nb_TN$NB_none*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 1000), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TN$threshold, form0_nb_TN$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TN$threshold, form4train_nb_TN$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 3 (LASSO - train) without grisk
  smooth2 <- smooth.spline(form0_nb_TN$threshold, form4gtrain_nb_TN$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 3 (LASSO - train) with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  legend("bottomright", legend = c("Treat none", "Original model", "Model revision (LASSO - train)", "Model revision with MammaPrint (LASSO - train)"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
  
# Method 3 - LASSO (test dataset)
  #Net TP
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TP$threshold,
       form0_nb_TP$NB_all*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 5), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TP$threshold, form0_nb_TP$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TP$threshold, form4test_nb_TP$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 3 (LASSO - test) without grisk
  smooth2 <- smooth.spline(form0_nb_TP$threshold, form4gtest_nb_TP$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 3 (LASSO - test) with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  abline(v=eventrate, col="black", lty=2)
  legend("topright", legend = c("Treat all", "Original model", "Model revision", "Model revision with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
  
  #Net TN
  par(las = 1, xaxs = "i", yaxs = "i")
  plot(form0_nb_TN$threshold,
       form0_nb_TN$NB_none*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net benefit (per 1000)",
       xlim = c(0, 0.15), ylim = c(-1, 1000), bty = "n",
       cex.lab = 1, cex.axis = 1)
  smooth0 <- smooth.spline(form0_nb_TN$threshold, form0_nb_TN$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TN$threshold, form4test_nb_TN$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 3 (LASSO - test) without grisk
  smooth2 <- smooth.spline(form0_nb_TN$threshold, form4gtest_nb_TN$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 3 (LASSO - test) with grisk
  abline(h=0, col="black", lwd=1)
  #abline(v=0.12, col="black", lty=2)
  legend("bottomright", legend = c("Treat none", "Original model", "Model revision", "Model revision with MammaPrint"),
         lwd = 3, cex = 1, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #title("MINDACT dataset (n=5920)", adj = 0.5, cex = 1.5)
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
```

# Combined decision curves
```{r DCA_plots_combined, fig.height=16, fig.width=15}
# Calculation of 5-year PREDICT event rate
eventrate <- 1 - summary(survfit(Surv(time, event) ~ 1, data = form0_riskdf), times = tmax)$surv

# Setting up graphical parameters common to all plots
par(las = 1, xaxs = "i", yaxs = "i", mar = c(5, 6, 4, 2) + 0.5)

# Plotting Net Benefit for True Positives (TP) across different methods
plotNetTP <- function(data1, data1g, method_label1, method_label2) {
  plot(form0_nb_TP$threshold,
       form0_nb_TP$NB_all*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "Threshold probability", ylab = "Net TP benefit (per 1000)",
       xlim = c(0, 0.16), ylim = c(-1, 5), bty = "n",
       cex.lab = 2, cex.axis = 2,
       mgp = c(3.5, 1, 0)) 
  smooth0 <- smooth.spline(form0_nb_TP$threshold, form0_nb_TP$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TP$threshold, data1$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 1 without grisk
  smooth2 <- smooth.spline(form0_nb_TP$threshold, data1g$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 1 with grisk
  abline(h=0, col="black", lwd=1)
  abline(v=eventrate, col="darkgray", lty=2)
  legend("topright", legend = c("Treat all", "Original model", method_label1, method_label2),
         lwd = 3, cex = 2, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
}

# Plotting Net Benefit for True Negatives (TN) across different methods
plotNetTN <- function(data1, data1g, method_label1, method_label2) {
    plot(form0_nb_TN$threshold,
       form0_nb_TN$NB_none*1000,
       type = "l", lwd = 3, lty = 1, col = "darkgray",
       xlab = "", ylab = "",
       xlim = c(0, 0.16), ylim = c(-1, 1000), bty = "n",
       cex.axis = 2)
  title(xlab = "Threshold probability", mgp = c(3.5, 1, 0), cex.lab = 2)
  title(ylab = "Net TN benefit (per 1000)", mgp = c(5, 1, 0), cex.lab = 2)
  smooth0 <- smooth.spline(form0_nb_TN$threshold, form0_nb_TN$NB*1000, spar=0.5)
  lines(smooth0, type = "l", lwd = 3, col="black")
  smooth1 <- smooth.spline(form0_nb_TN$threshold, data1$NB*1000, spar=0.5)
  lines(smooth1, type = "l", lwd = 3, col="orange") #NB of Method 1 without grisk
  smooth2 <- smooth.spline(form0_nb_TN$threshold, data1g$NB*1000, spar=0.5)
  lines(smooth2, type = "l", lwd = 3, col="blue") #NB of Method 1 with grisk
  abline(h=0, col="black", lwd=1)
  legend("bottomright", legend = c("Treat none", "Original model", method_label1, method_label2),
         lwd = 3, cex = 2, col = c("darkgray", "black", "orange", "blue"), bty = "n")
  #rect(xleft = 0.05, xright = 0.15, ybottom = par("usr")[3], ytop = par("usr")[4],
  #     border = NA, col = adjustcolor("grey", alpha = 0.3))
}

layout(matrix(1:6, nrow = 3, ncol = 2, byrow = TRUE))

plotNetTP(form1_nb_TP, form1g_nb_TP, "Recalibration-in-the-large", "Recalibration-in-the-large with MammaPrint")
title(main = "A", adj = 0, line = 1, cex.main = 2)
plotNetTN(form1_nb_TN, form1g_nb_TN, "Recalibration-in-the-large", "Recalibration-in-the-large with MammaPrint")
title(main = "B", adj = 0, line = 1, cex.main = 2)

plotNetTP(form2_nb_TP, form2g_nb_TP, "Recalibration ", "Recalibration with MammaPrint")
title(main = "C", adj = 0, line = 1, cex.main = 2)
plotNetTN(form2_nb_TN, form2g_nb_TN, "Recalibration ", "Recalibration with MammaPrint")
title(main = "D", adj = 0, line = 1, cex.main = 2)

plotNetTP(form4test_nb_TP, form4gtest_nb_TP, "Revision", "Revision with MammaPrint")
title(main = "E", adj = 0, line = 1, cex.main = 2)
plotNetTN(form4test_nb_TN, form4gtest_nb_TN, "Revision", "Revision with MammaPrint")
title(main = "F", adj = 0, line = 1, cex.main = 2)
```

# NB at specific thresholds
```{r NB_at_thresholds}
nb_at_thresholds <- function(nb_thresholds) {
  
  # Create a list of NB dataframes
  data_frames <- list(
  form0_nb_TP, #Method 0 - original model
  form1_nb_TP, form1g_nb_TP, #Method 1 - recalibration-in-the-large
  form2_nb_TP, form2g_nb_TP, #Method 2 - recalibration
  form3_nb_TP, form3g_nb_TP, #Method 3 - backward selection with shrinkage
  form4train_nb_TP, form4gtrain_nb_TP, #Method 3 - LASSO revision (train data)
  form4test_nb_TP, form4gtest_nb_TP) #Method 3 - LASSO revision (test data)

  # Add labels
  data_frame_names <- c(
    "Original model",
    "1", "1 with grisk",
    "2", "2 with grisk",
    "3 (backward selection)", "3 with grisk (backward selection)",
    "3 (LASSO) - train", "3 with grisk (LASSO) - train",
    "3 (LASSO) - test", "3 with grisk (LASSO) - test")
  
  # Loop through list of NB dataframes
  for (i in seq_along(data_frames)) {
    df <- data_frames[[i]]
    df_name <- data_frame_names[i]
    df$threshold <- as.character(df$threshold)
    
    # Round columns and calculate NB per 1000 persons
    df[, -1] <- round(df[, -1] * 1000, 0)
    
    # Output
    cat("Method:", df_name, "\n")
    cat("Thresholds:", nb_thresholds, "\n\n")
    cat(df$NB[df$threshold %in% nb_thresholds], "\n\n")
    }
}

nb_at_thresholds(nb_thresholds = c(0.030, 0.050, 0.100, 0.120, 0.150))

nb_at_thresholds_TN <- function(nb_thresholds) {
  
  # Create a list of NB dataframes
  data_frames <- list(
  form0_nb_TN, #Method 0 - original model
  form1_nb_TN, form1g_nb_TN, #Method 1 - recalibration-in-the-large
  form2_nb_TN, form2g_nb_TN, #Method 2 - recalibration
  form3_nb_TN, form3g_nb_TN, #Method 3 - backward selection with shrinkage
  form4train_nb_TN, form4gtrain_nb_TN, #Method 3 - LASSO revision (train data)
  form4test_nb_TN, form4gtest_nb_TN) #Method 3 - LASSO revision (test data)

  # Add labels
  data_frame_names <- c(
    "Original model",
    "1", "1 with grisk",
    "2", "2 with grisk",
    "3 (backward selection)", "3 with grisk (backward selection)",
    "3 (LASSO) - train", "3 with grisk (LASSO) - train",
    "3 (LASSO) - test", "3 with grisk (LASSO) - test")
  
  # Loop through list of NB dataframes
  for (i in seq_along(data_frames)) {
    df <- data_frames[[i]]
    df_name <- data_frame_names[i]
    df$threshold <- as.character(df$threshold)
    
    # Round columns and calculate NB per 1000 persons
    df[, -1] <- round(df[, -1] * 1000, 0)
    
    # Output
    cat("Method:", df_name, "\n")
    cat("Thresholds:", nb_thresholds, "\n\n")
    cat(df$NB[df$threshold %in% nb_thresholds], "\n\n")
    }
}

nb_at_thresholds_TN(nb_thresholds = c(0.030, 0.050, 0.100, 0.120, 0.150))
```
